---
title: projecter
author: "Chris Donovan\n"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
    github_document:
        toc: true
        toc_depth: 1
        html_preview: true
    html_document:
        toc: true
        toc_depth: 1
        number_sections: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Introduction

The projecter package is a small collection of functions that make my life easier. It contains some wrappers with somewhat sensible defaults for setting up a README, Rprofile, and Table of Contents scripts. The main function is `project()`, which does all three. The package also contains some convenience functions for wrangling data. This is very much a work in progress, and mostly set up for my own peace of mind. But feel free to yoink anything you like.

# Installation

You can install the development version of projecter from GitHub with:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("ChrisDonovan307/projecter")
```

# How to Project
